Title

### 2014-07-24 paper.tex
Result: RQ1 (roughly done)

\documentclass[conference]{IEEEtran}
\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfig,paralist,graphicx}
%\usepackage{flushend}

\usepackage[font=small,labelfont=bf]{caption}

\usepackage{xspace}
\usepackage{color}
\usepackage{ifthen}
\usepackage{url}
\usepackage{fancybox}

@@

For our empirical study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process. Our case study project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation. To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy. We also used our predictive model for the all set of comments to preliminary estimate quality of reviews. According to this, we address the following two research questions:

@@

To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
\begin{itemize}
\item \textbf{useful}$(c,S_T,D_T)= \mathrm{TRUE}$ if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
\item \textbf{useless}$(c,S'_T,D'_T)= \mathrm{TRUE}$  if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
\end{itemize}
where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification. The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review. The details our approach is described in the following subsections.

@@

\begin{equation}
w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
\label{eq:tf-idf}
\end{equation}
\pick{Equation need to be check.}

After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance. 
\pick{Why we need two measurements?}

@@

\begin{equation}
\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
\label{eq:euclid}
\end{equation}
\subsection{Manual useful comments identification}

\subsection{Estimating Similarity and Dissimilarity Threshold}
To find similarity and dissimilarity thresholds, we iteratively measure an accuracy for values of $S_T$ and $S'_T$ raging $[0,1]$; and values of $D_T$ and $D'_T$ ranging $[0,\infty)$. We define that the best similarity and dissimilarity thresholds are the set of define values can maximize accuracy value. In this study, we use F-measure score for an accuracy measure. The F-measure value can be calculated using Equation \ref{}

\begin{equation}
\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
\label{eq:precision}
\end{equation}
where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
%According to this, we can formalize as follows:

@@

\section{Case Study}

% where we got the data
We used the review data sets of the Qt project collected by Hamasaki et al \TODO{cite properly}.
Only reviews in the master branch of \texttt{qtbase} project are considered,
as it is the most active branch.

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

% overview
In our classification method,
all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
Few comments are sampled and then classified manually for use in training and validation.
A model is created from these training data, from which useful comments can automatically be identified.
This process is illustrated in Fig.\ref{fig:overview}.

\subsection{Data Preparation}

The commit messages and all comment texts are converted into vectors as part of the preparation step.
Fig. \ref{fig:preprocess} illustrates the overview of this step.
We wrote scripts in Ruby language to perform these tasks.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{preprocess}
\caption{The data preparation process.
Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
and are converted into a vector.}
\label{fig:preprocess}
\end{figure}

\subsubsection{Removal of automatically generated text}

First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.

% conversion into vector, wow
Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
This effectively removed the ID numbers and other non-generic terms.

Next, the lines that appears most frequently are identified.
From these lines, we then constructed the regular expression patterns,
and finally, these patterns are used to filter out automatically generated text from our data.

\subsubsection{Tokenization, stop word removal and stemming}

After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
The stemming is performed on remaining tokens using Porter stemming algorithm.
The remaining words are then combined to form a corpus of all used words.

\subsubsection{Conversion into vector}

Finally, the tf--idf algorithm is used to convert each document into a vector.

\subsection{Training Data}

We sampled 320 comments from the data set.
These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
This task is carried out by three people who worked independently.

Each comment is then scored based on the number of positive answers.
For example, a comment with a score of 3 means that all three people said that it is useful,
while a comment with a score of 0 means that none of us marked it as useful.

@@

\subsection{Model Generation and Validation}

% the metrics
For each comment, we computed similarity and dissimilarity metrics
between the comment text and the corresponding commit message.
We chose cosine similarity and euclidean distance as the metrics to use in model generation.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{vector}
\caption{The similarity and distance metric that is being used.}
\label{fig:vector}
\end{figure}

% assumptions in categorization
The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}

% finding parameters
To find these parameters, a brute-force approach is used.
This is possible because the set of $similarity$ and $distance$ values are discrete.
Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.

% validation
To validate our model, we randomly split the data into 10 parts.
9 parts are used for training, and 1 part for validation.
This process is repeated 300 times. % while I sleep
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
to give the overall performance of our model.

\section{Results}

\subsection{Data Preparation}

\begin{figure}[h]
\centering
\includegraphics[width=3.2in]{filter}
\caption{The filtering process.}
\label{fig:filter}
\end{figure}

\subsubsection{Data extraction}

6,605 changes and 72,484 comments have been extracted from the raw dataset.
35\% of the comments are by the system or one of the bots, and are thus discarded.

\subsubsection{Common pattern removal}

By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.

Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
This probably means these comments solely contain automatically-generated text, and are thus discarded.
This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.

\subsubsection{Tokenizing}

After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.

\subsection{Training Data}

After the 320 sample comments have been labeled,
they are scored based on the number of ``yes'' given to the sample.
There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.

After the similarity and distance metrics have been calculated,
these metrics appear to be able to separate the useful comments from the non-useful ones,
as can be seen in Fig.\ref{fig:scatter}.
Note that many comments have a cosine similarity metric of 0.
This is because the comment text and the corresponding commit message has no word in comment.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{scatter}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

\subsection{Model Generation}

% the criteria that were found
From our training data,
the following criteria have been obtained that maximizes the F$_1$ score:

Criteria to find samples with score of 3 (``positive''):
\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
\\ \text{(F$_1$-score: 0.741313)} \end{gather*}

Criteria to find samples with score of 0 (``negative''):
\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
\\ \text{(F$_1$-score: 0.725389)}\end{gather*}

Note that these constant values can vary from project to project, and thus is not a universal constant.

% run result

Running our model against the training data gives us the result displayed in the following table.
In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.

\begin{center}
\begin{tabular}{|r|rrrr|}
\hline
& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
\hline
Negative & 69 & 23 & 7 & 6 \\
Neither & 12 & 24 & 20 & 20 \\
Overlap & 1 & 1 & 0 & 1 \\
Positive & 4 & 13 & 24 & 95 \\
\hline
\end{tabular}
\end{center}

As expected, most comments classified as \emph{negative} have score of 0 and 1,
while most \emph{positive} comments have score of 2 and 3.
However, some comments in every score type were classified as \emph{neither}.

@@

\subsection{Cross Validation}

After we performed cross validation, we obtained the following result:
for positive and negative classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,balance,makecell,algorithm,algorithmic,subfigure,paralist}
%\usepackage{flushend}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{url}
\usepackage[font=small,labelfont=bf]{caption}

\usepackage{xspace}
\usepackage{color}
\usepackage{ifthen}
\usepackage{fancybox}

@@

For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process. Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation. To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy. We also used our predictive model for the all set of comments to preliminary estimate quality of reviews. According to this, we address the following two research questions:

@@

To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
\begin{itemize}
\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
\end{itemize}
where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification. The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review. The details our approach is described in the following subsections.
\pick{Why we need two measurements?}
\pick{What happen in model for otherwise?}

@@

\begin{equation}
w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
\label{eq:tf-idf}
\end{equation}

After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.

@@

\begin{equation}
\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
\label{eq:euclid}
\end{equation}

\subsection{Estimating Similarity and Dissimilarity Threshold}
We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$. This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall). This can be calculated using Equation \ref{eq:fmeasure}.

\begin{equation}
\begin{split}
\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
\\
\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
\\
\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
\end{split}
\label{eq:fmeasure}
\end{equation}

Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful. To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments. For the correctness of prediction, we determine from the useful/useless defined dataset.

%Using this method, we iteratively measure an accuracy for values of $s_t$ and $s'_t$ ranging $[0,1]$; and values of $d_t$ and $d'_t$ ranging $[0,\infty)$.

%\begin{equation}
%\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
%\label{eq:precision}
%\end{equation}

%where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
%According to this, we can formalize as follows:

@@

\section{Case Study Design}

We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of small subsystems. For our case study, we selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

% where we got the data
%We used the review data sets of the Qt project collected by Hamasaki et al\cite{Hamasaki2013}.
%Only reviews in the master branch of \texttt{qtbase} project are considered,
%as it is the most active branch.

% quick structure
%\pick{This already explain in background :D}
%Each change includes a \emph{commit message} which describes what is changed.
%After a change is submitted to Gerrit, reviewers can give scores to it.
%The scores will determine whether the change will be accepted or not.
%Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
%Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

% overview
%In our classification method,
%all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
%Few comments are sampled and then classified manually for use in training and validation.
%A model is created from these training data, from which useful comments can automatically be identified.
%This process is illustrated in Fig.\ref{fig:overview}.
%

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set. We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.

%The commit messages and all comment texts are converted into vectors as part of the preparation step.
%Fig. \ref{fig:preprocess} illustrates the overview of this step.
%We wrote scripts in Ruby language to perform these tasks.

%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{preprocess}
%\caption{The data preparation process.
%Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
%and are converted into a vector.}
%\label{fig:preprocess}
%\end{figure}

%\subsubsection{Removal of automatically generated text}
%
%First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
%
%% conversion into vector, wow
%Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
%This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
%This effectively removed the ID numbers and other non-generic terms.
%
%Next, the lines that appears most frequently are identified.
%From these lines, we then constructed the regular expression patterns,
%and finally, these patterns are used to filter out automatically generated text from our data.

\subsubsection{Data Preprocessing}
 we extracted semantic words commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

%After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
%Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
%The stemming is performed on remaining tokens using Porter stemming algorithm.
%The remaining words are then combined to form a corpus of all used words.

%\subsubsection{Conversion into vector}
%
%Finally, the tf--idf algorithm is used to convert each document into a vector.

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, we read comments and manually identified useful and useless comments. In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''. Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless. From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \textbf{useless} comments. For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.

\subsection{Research Questions}
To validate our approach, we addressed the following research questions:

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach. We also determined the robustness of our approach using cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for test set.
The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.

Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).

%We sampled 320 comments from the data set.
%These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
%This task is carried out by three people who worked independently.
%
%Each comment is then scored based on the number of positive answers.
%For example, a comment with a score of 3 means that all three people said that it is useful,
%while a comment with a score of 0 means that none of us marked it as useful.

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set. We then used these thresholds to classify the rest of comments. A statical analysis was performed to understand the impact of useful discussion to software quality.

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
\indent

%\subsection{Training Data}

@@

%\pick{I re-wrote of these, hope I don't miss something ;)}
%\subsection{Model Generation and Validation}
%
%% the metrics
%For each comment, we computed similarity and dissimilarity metrics
%between the comment text and the corresponding commit message.
%We chose cosine similarity and euclidean distance as the metrics to use in model generation.
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{vector}
%\caption{The similarity and distance metric that is being used.}
%\label{fig:vector}
%\end{figure}
%
%% assumptions in categorization
%The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
%and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
%where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
%
%% finding parameters
%To find these parameters, a brute-force approach is used.
%This is possible because the set of $similarity$ and $distance$ values are discrete.
%Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
%
%% validation
%To validate our model, we randomly split the data into 10 parts.
%9 parts are used for training, and 1 part for validation.
%This process is repeated 300 times. % while I sleep
%The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
%to give the overall performance of our model.

\section{Case Study Results}
\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.

\begin{table}[!h]
\caption{A summary data sets and some statistics.}
\centering
\small
\begin{tabular}{ccc}
\hline
& Total Number & Percentage \\ \hline \hline
Commit Messages & 6,605 &  -  \\ \hline
All Comments & 72,484& - \\ \hline
Reviewers Messages & 10,670 & 15\% \\ \hline
Automated Messages. & 61,814 & 85\% \\ \hline

\end{tabular}
\label{tb:datastatistic}
\end{table}

%\pick{I realize that your figure is better for the presentation :)}
%\begin{figure}[h]
%\centering
%\includegraphics[width=3.2in]{filter}
%\caption{The filtering process.}
%\label{fig:filter}
%\end{figure}
%\subsection{Data Preparation}
%\subsubsection{Data extraction}
%
%6,605 changes and 72,484 comments have been extracted from the raw dataset.
%35\% of the comments are by the system or one of the bots, and are thus discarded.
%
%\subsubsection{Common pattern removal}
%
%By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
%
%Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
%This probably means these comments solely contain automatically-generated text, and are thus discarded.
%This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
%
%\subsubsection{Tokenizing}
%
%After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
%This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
%

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}

From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. \pick{We cannot brute force for every floating number. How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score. \pick{I used dummy results. Please change it} \pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

\textbf{Model Effectiveness.} Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds. The green area represents useful model $\Theta(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$ and the red area represents useless classification model $\Omega(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$. This figure also shows an example comment that fall in the different area\pick{Didn't put yet}. As shown in the figure, most of comments fall in green area is useful comments and very few useless comments fall in this area. Similarly, most of comments fall in red area is useless comments. However, some comments were not determined (in white area). From the example comment, it shows that these comments discussed on ..... which did not contains any similar words. Moreover, the areas of these two models are overlap. Table \ref{tb:classify_number} summarizes the number of classification from this results. Interestingly, 87\% useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores. This is same as the results of useful class that most of them have \texttt{YES} = 2 and 3 voting scores
This finding suggests that these unclear comments have something.....

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data }
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 4 & 13 & 24 & 95 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 20 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
\multirow{7}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline \hline
\multirow{7}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
for useful and useless classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.
This indicates that we can use our approach to classify with confident of 69.8\%.
\pick{Precision? Recall?}

According to the results, we can answer  RQ1 that \textit{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}

%After we performed cross validation, we obtained the following result:
%for positive and negative classifications,
%we obtained an average F$_1$ score of 0.693 and 0.681,
%with standard deviation of 0.090 and 0.118, respectively.
%This indicates that we can use our approach to classify with confident of 69.8\%.

%After the similarity and distance metrics have been calculated,
%these metrics appear to be able to separate the useful comments from the non-useful ones,
%as can be seen in Fig.\ref{fig:scatter}.
%Note that many comments have a cosine similarity metric of 0.
%This is because the comment text and the corresponding commit message has no word in comment.

\begin{figure}[!t]
\centering
\includegraphics[scale=0.55, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}

\pick{If there is high \% of useless messages, it means ineffective review, isn't it?}

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\

%\subsection{Model Generation}

%% the criteria that were found
%From our training data,
%the following criteria have been obtained that maximizes the F$_1$ score:
%
%Criteria to find samples with score of 3 (``positive''):
%\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
%\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
%
%Criteria to find samples with score of 0 (``negative''):
%\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
%\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
%
%Note that these constant values can vary from project to project, and thus is not a universal constant.
%
%% run result
%
%Running our model against the training data gives us the result displayed in the following table.
%In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
%
%\begin{center}
%\begin{tabular}{|r|rrrr|}
%\hline
%& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
%\hline
%Negative & 69 & 23 & 7 & 6 \\
%Neither & 12 & 24 & 20 & 20 \\
%Overlap & 1 & 1 & 0 & 1 \\
%Positive & 4 & 13 & 24 & 95 \\
%\hline
%\end{tabular}
%\end{center}
%
%As expected, most comments classified as \emph{negative} have score of 0 and 1,
%while most \emph{positive} comments have score of 2 and 3.
%However, some comments in every score type were classified as \emph{neither}.
%
%

@@
